---
title: "p8105_hw6_zl3263"
output: github_document
date: "2022-12-03"
---

### Problem 2

```{r}
library(tidyverse)
library(corrplot)
library(modelr)
```

**load data**
```{r}
homicides = read_csv("https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv")%>%
   janitor::clean_names() %>%
   mutate(
    city_state = paste(city,",",state)
  ) %>%
  filter(
    victim_race != "Unknown",
    city_state != "Tulsa , AL",
    victim_age != "Unknown",
    victim_sex != "Unknown"
    
  ) %>%
  mutate(
    victim_age = as.numeric(victim_age)
  ) 
  
  
```
**modeling on baltimore**
```{r}
baltimore = homicides %>%
  filter(
    victim_race == "Black" | victim_race == "White",
    city_state == 'Baltimore , MD',
  ) %>%
  mutate(
    resolved = as.numeric(disposition == "Closed by arrest")
  )

model_logistic = glm(resolved ~ victim_age + victim_sex + victim_race, data = baltimore, family = binomial() )

model_logistic %>% 
  broom::tidy() %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>%
  select(term, estimate, CI_lower, CI_upper, OR)

```

**modeling on each city**
```{r}
fit_others = homicides %>%
  filter(
    victim_race == "Black" | victim_race == "White",
  ) %>%
  mutate(
    resolved = as.numeric(disposition == "Closed by arrest")
  ) %>%
  nest(nested = -city_state) %>% 
  mutate(
    models = map(.x = nested, ~glm(resolved ~ victim_age + victim_sex + victim_race, data = .x, family = binomial())),
    outputs = map(models, broom::tidy)
    ) %>%
  select(city_state, outputs) %>% 
  unnest(outputs) %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(city_state, term, estimate, CI_lower, CI_upper, OR) %>%
  filter(
    term == "victim_sexMale"
  )

fit_others %>%
  head() %>%
  knitr::kable(digits = 3)
```

**plot**
```{r}
fit_others %>%
  ggplot(aes(x = reorder(city_state, OR), y = OR)) +
	  geom_point() +
	  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper)) +
	  labs(
	  	x = "Cities",
	  	y = "ORs with Confidence Intervals",
	  ) +
	  theme(
	  	axis.text.x = element_text(angle = 90)
	  )
```

**comments**

In most of the cities, homicides in which the victim is male are less likely to be resolved than those in which the victim is female. But for cities after Atlanta shown on the plot above, homicides with female victim are less likely to be resolved.

### Problem 3

**load and clean the data**

```{r}
birth_weight = read_csv("https://p8105.com/data/birthweight.csv") %>%
  janitor::clean_names() %>%
  filter(
    frace < 8,
    mrace < 8
  ) %>%
  mutate(
    babysex = as.factor(babysex),
    frace = as.factor(frace),
    mrace = as.factor(mrace),
    malform = as.factor(malform)
  ) 

head(birth_weight)  
  
```
**trying to select varaibles**
```{r}
read_csv("https://p8105.com/data/birthweight.csv") %>% 
  cor() %>%
  corrplot(,type = "lower")
```

I choose 3 variables that have highest correlation coefficient with `bwt`, since they all positively related, I also add a negatively related variable to my model.

**model 1**
```{r}
model1 = lm(bwt ~ bhead + blength + gaweeks + mrace, data = birth_weight)

birth_weight %>% 
  add_residuals(model1) %>%
  add_predictions(model1) %>% 
  ggplot(aes(x = pred, y = resid)) + 
  geom_point(alpha = 0.5) +
  geom_smooth(se = F, color = "red", method = "lm")

  
```

```{r}
model2 = lm(bwt ~ blength + gaweeks, data = birth_weight) 

model3 = lm(bwt ~ bhead + blength + babysex + bhead:blength + blength:babysex + bhead:babysex + bhead:blength:babysex, data = birth_weight) 
```

**cross validation**

```{r}
cv_df = 
  crossv_mc(birth_weight, 100) 

cv_df =
  cv_df %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble))

cv_df = 
  cv_df %>% 
  mutate(
    model1  = map(train, ~lm(bwt ~ bhead + blength + gaweeks + mrace, data = .x)),
    model2  = map(train, ~lm(bwt ~ blength + gaweeks, data = .x)),
    model3  = map(train, ~lm(bwt ~ bhead + blength + babysex + bhead:blength + blength:babysex + bhead:babysex + bhead:blength:babysex, data = .x))
    ) %>% 
  mutate(
    rmse_model1 = map2_dbl(model1, test, ~rmse(model = .x, data = .y)),
    rmse_model2 = map2_dbl(model2, test, ~rmse(model = .x, data = .y)),
    rmse_model3 = map2_dbl(model3, test, ~rmse(model = .x, data = .y))
    )

cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin()
```

According to the plot, model 3 and model 1 have better performance than model 2.
